{CPU-Scheduling}

### 2024-12-11 LaTeX/Sources/Advanced.tex
added multiple processes mlfq

\chapter{Predicting the Future based on the Past}

@@

The first policy we look at is formerly called Multi-Level Feedback Queue or MLFQ short. The create Fernando J. Corbató recieved a Turning Awaard for it in 1990. 
As the title already says, this policy tries to predict the future behaviour of the processes based on the past.
A job can be generally act in two ways.
Either it is a resources intensive crunching problem (think about exporting a video or compiling code) or it is a program, which needs quick response time (think about your text editor).
In reality most jobs jump between these two states.
We usually want to give the response based processes priority, because that is what the user interacts with and it is here that he primarily feels a delay.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{Assets/MLFQ-Example-1.pdf}
    \caption{Simple working of MLFQ}
    \label{fig:mlfq-example-1}
\end{figure}

@@

>>>>

\chapter{Predicting the Future}

@@

The first policy we look at is formerly called Multi-Level Feedback Queue or MLFQ short. The create Fernando J. Corbató recieved a Turning Award for it in 1990. 
As the title already says, this policy tries to predict the future behaviour of the processes based on the past.
A job can be generally act in two ways.
Either it is a resources intensive crunching problem (think about exporting a video or compiling code) or it is a program, which needs quick response time (think about your text editor).
In reality most jobs jump between these two states.
We usually want to give the response based processes priority, because that is what the user interacts with and it is here that he primarily feels a delay.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{Assets/MLFQ-Example-1.pdf}
    \caption{Simple working of MLFQ}
    \label{fig:mlfq-example-1}
\end{figure}

@@

\section{Multiple Processes}

What happens if we introduce another process?
Well, it depends on the priorities. 
Higher priority recieves the CPU time.
If they are on the same queue, than they run using Round Robin, see section \ref{sec:rr}.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{Assets/MLFQ-Example-2.pdf}
    \caption{Running multiple processes in MLFQ}
    \label{fig:mlfq-example-2}
\end{figure}

As you can see in figure \ref{fig:mlfq-example-2} once process two is introduced process one is temporarily starved. The problem is solved once they land on the same queue.
There they run alternately.
Still the more tasks we introduce the more prevalent the starving issue gets.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{Assets/MLFQ-Example-3.pdf}
    \caption{Starving Processes in MLFQ}
    \label{fig:mlfq-example-3}
\end{figure}
